#### Imports

```{r}
library(Rmisc)
library(tidyverse)
library(stringr)
library(scales)
library(grid)
library(ggpubr)
library(MASS)
library(lme4)
library(stats)
library(modelr)
library(plotrix)
library(mgcv)
library(hexbin)
library(formattable)
library(MuMIn)
library(ggrepel)
library(data.table)
library(comprehenr)
library(ggplot2)
library(dplyr)
library(car)
library(sjPlot)

source("utils.R")
```

#### Definitions

```{r}
data_dir <- "../data/provo_RT_test_preprocessed_exp1_4_0.csv"
goal <- "GPT"

candidates <- c("surprisal", "attention_entropy", "attention_distance", "attention_difference", "attention_activation")
baseline_predictors <- c("frequency", "length", "position", "lemma", "element")
```

#### Data Preparationscaling_var

```{r}

data <- read.csv(data_dir)

# Get names of numeric columns
numeric_cols <- names(data)[sapply(data, is.numeric)]
# Subset to numeric columns you want to scale
excluded_vars <- c(goal, "WorkerId", "item", "element", "zone", "chunksentence")

cols_to_scale <- setdiff(numeric_cols, excluded_vars)

# Apply cut-off
# Provo already comes with a minimal value of 81 for GPT
data <- apply_cutoff(data, goal)

# Remove outliers
data <- remove_outliers(data, c(goal), id_col="WorkerId")

# Apply scaling
data <- data %>%
  dplyr::mutate(
    dplyr::across(
      dplyr::all_of(cols_to_scale),
      scaling_var,
      .names = "{.col}.s"
    )
  )
```

For eye-tracking, we remove skipped-over words as they do not inform us about comprehension process durations.

#### Simple check of aggregated correlation

```{r}
compute_mean <- function(datasets, factor1, factor2) {
  formula_str <- paste("cbind(", factor1, ",", factor2, ") ~ item + zone")
  means <- aggregate(as.formula(formula_str), data=data, FUN = mean, na.rm = TRUE)
  corr <- cor.test(means[[factor1]], means[[factor2]], method="pearson")
  corr
}

compute_mean(data, "GPT", "surprisal")
compute_mean(data, "GPT", "attention_entropy")
```

#### First check of assumptions

We check for collinearity and multicollinearity of the variables:

##### Pairwise collinearity:

We check this via a correlation matrix:

```{r}

preds <- data %>%
  dplyr::select(frequency, length, position, Text_ID, Sentence_Number, Word_Number)
cor_mat <- cor(preds)
round(cor_mat, 2)
```

We may have a problem for frequency-length.

##### Multicollinearity:

We detect multicollinearity using VIF. Thresholds are motivated by: <https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/j.2041-210X.2009.00001.x>

TODO

```{r}
m <- lm(GPT ~ frequency + length + position + Text_ID + Sentence_Number + Word_Number, data)
vif(m)
```

There is cause to worry about Sentence_Number and Word_Number. Word_Number is almost 5; we will leave it out. It likely correlated with a combination of position and Sentence_number.

#### Baseline model

We should include predictors frequency and length. But what about position, text number and sentence number (nested inside text numer)? We perform a first preliminary test without random effects:

```{r}
#| cache = TRUE

m <- lm(GPT ~ frequency.s + length.s + position.s + Text_ID.s + Sentence_Number.s,
  data=na.omit(data))
summary(m)
```

The coefficient for Text_ID is very small. Let's check for significance:

```{r}
m0 <- lm(GPT ~ frequency.s + length.s + position.s + Sentence_Number.s,
  data=na.omit(data))
anova(m0, m)
```

We definitely cannot refute the null hypothesis. Thus, we will not include it. We will check later if it should be a group.

##### Random effects

Now, let's include random effects. We will use some tricks to speed up the fitting.

Let's start with random effects based on subjects since these are well motivated:

```{r}
lmer(GPT ~ frequency.s + length.s + position.s + Sentence_Number.s + (frequency.s + length.s + position.s + Sentence_Number.s | WorkerId),
  data=na.omit(data),
  REML=FALSE,
  lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))
```

We have convergence issues likely connected to the Sentence_Number random slope. Let's try refitting without it:

```{r}
lmer(GPT ~ frequency.s + length.s + position.s + Sentence_Number.s + (frequency.s + length.s + position.s | WorkerId),
  data=na.omit(data),
  REML=FALSE,
  lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))
```

That worked. Now, we will not add random effects for each item since we do not have any predictors that vary by item. But we can generalise items by word forms.

Here, we make it a bit easier and normalise by taking the lemma as a grouping level. We will not add frequency and length random slopes for lemmata even since the lemma groups are our normalised surrogate for the "word" column. Although frequency and length are not the same for all word forms of a lemma, including these would be redundant and slopes would not be well motivated.

This results in crossed effects:

```{r}
#| cache = TRUE

lmer(GPT ~ frequency.s + length.s + position.s + Sentence_Number.s + (frequency.s + length.s + position.s | WorkerId) + (position.s + Sentence_Number.s | lemma),
  data=na.omit(data),
  REML=FALSE,
  lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))
```

Again, there are convergence issues. We remove the correlation matrix for lemmata.

```{r}
#| cache = TRUE

lmer(GPT ~ frequency.s + length.s + position.s + Sentence_Number.s + (frequency.s + length.s + position.s | WorkerId) + (position.s + Sentence_Number.s || lemma),
  data=na.omit(data),
  REML=FALSE,
  lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))
```

This seems to work well. Finally, let's check if we can fit the model with random effects based on Text_Id:

```{r}
#| cache = TRUE

lmer(GPT ~ frequency.s + length.s + position.s + Sentence_Number.s + (frequency.s + length.s + position.s | WorkerId) + (position.s + Sentence_Number.s || lemma) + (frequency.s + length.s + position.s + Sentence_Number.s | Text_ID),
  data=na.omit(data),
  REML=FALSE,
  lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))
```

We need to simplify the structure again:

```{r}
#| cache = TRUE

m <- lmer(GPT ~ frequency.s + length.s + position.s + Sentence_Number.s + (frequency.s + length.s + position.s | WorkerId) + (position.s + Sentence_Number.s || lemma) + (frequency.s + length.s + position.s + Sentence_Number.s || Text_ID),
  data=na.omit(data),
  REML=FALSE,
  lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))
m
```

The estimated fixed effect for position is really small. Let's check whether it is significant.

```{r}
m0 <- lmer(GPT ~ frequency.s + length.s + Sentence_Number.s + (frequency.s + length.s + position.s | WorkerId) + (position.s + Sentence_Number.s || lemma) + (frequency.s + length.s + position.s + Sentence_Number.s || Text_ID),
  data=na.omit(data),
  REML=FALSE)

m0
```

```{r}
anova(m0, m)
```

Based on this result, we do not include position. What about sentence number?

```{r}
m0 <- lmer(GPT ~ frequency.s + length.s + (frequency.s + length.s | WorkerId) + (Sentence_Number.s || lemma) + (frequency.s + length.s + Sentence_Number.s || Text_ID),
  data=na.omit(data),
  REML=FALSE)
m0
```

```{r}
m1 <- lmer(GPT ~ frequency.s + length.s + Sentence_Number.s + (frequency.s + length.s | WorkerId) + (Sentence_Number.s || lemma) + (frequency.s + length.s + Sentence_Number.s || Text_ID),
  data=na.omit(data),
  REML=FALSE)
m1
```

```{r}
anova(m0, m1)
```

Good. Therefore, we also leave out Sentence_Number as a covariate. How about reintroducing the correlations between random coefficients in the Text_ID group?

```{r}
m <- lmer(GPT ~ frequency.s + length.s + (frequency.s + length.s | WorkerId) + (frequency.s + length.s | Text_ID),
  data=na.omit(data),
  REML=FALSE)
summary(m)
```

We fix this model for now.

#### Second check of assumptions

We need to check the following assumptions for meaningful tests with LMEs:

1.  Linearity: The relationship between the predictors and the dependent variable should be linear.
2.  Normality of residuals: The residuals should be normally distributed.
3.  Homogeneity of variances: The variance of the residuals should remain constant across all levels of the predictors.
4.  Normality of random effects: The random effects should be normally distributed.

See: <https://speeds.quarto.pub/speeds/regression_4_LMM.pdf> (TODO)

##### Linearity of predictors

We perform a quick visual inspection:

```{r}
plot(fitted(m), resid(m))
abline(h = 0)
```

We see a slope on the bottom left due to the cut-off in the Provo dataset. Furthermore, residuals disperse more to the top than to the bottom indicating that among extreme cases underpredictions of GPT are more common than overpredictions.

The shape in the lower left suggests that another kind of modelling might be sensible that does not predict values smaller than the lower cut-off point (or even negative values). However, that would introduce additional complexity. Besides this feature the cloud suggests mild nonlinearity at best.

Let's plot fitted values (keeping in mind that their interpretation may be problematic since they keep all predictors constant except for one predictor of interest.

```{r}
plot_bins(m, "frequency.s", bins=25, data=data)
plot_bins(m, "length.s", bins=25, data=data)
```

Length seems alright. Frequency appears to be influenced by some extremely low frequency items. TODO

##### Normality of residuals

```{r}
qqnorm(resid(m))
qqline(resid(m))
hist(resid(m))
```

Most residuals are negative and we have a right tail. The Q-Q plot exhibits a dent. Possibly log transformation can help.

##### Homogeneity of variances

```{r}
plot(data$frequency.s, resid(m)); abline(h=0,lty=2)
plot(data$length.s, resid(m)); abline(h=0,lty=2)
```

We can see the right tail manifested at high frequency and at low length words, i.e. those are predicted too low.

Furthermore, we see artifacts that are caused by frequency, probably by some very infrequent words where the wordfreq library couldn't generate a reliable measure. Therefore, we will remove values smaller than 2.

##### Normality of random effects

```{r}
re <- ranef(m)
qqnorm(re$WorkerId[,1]); qqline(re$WorkerId[,1])
qqnorm(re$WorkerId[,2]); qqline(re$WorkerId[,2])
qqnorm(re$WorkerId[,3]); qqline(re$WorkerId[,3])
qqnorm(re$Text_ID[,1]); qqline(re$Text_ID[,1])
qqnorm(re$Text_ID[,2]); qqline(re$Text_ID[,2])
qqnorm(re$Text_ID[,3]); qqline(re$Text_ID[,3])
```

The Text_Id effects are normal. WorkerId effects show signs of nonlinearity.

##### Removing problematic frequencies and introducing interactions

```{r}
data <- read.csv(data_dir)

# Get names of numeric columns
numeric_cols <- names(data)[sapply(data, is.numeric)]
# Subset to numeric columns you want to scale
excluded_vars <- c(goal, "WorkerId", "item", "element", "zone", "chunksentence")
cols_to_scale <- setdiff(numeric_cols, excluded_vars)

# Apply cut-off
# Provo already comes with a minimal value of 81 for GPT
data <- apply_cutoff(data, goal)
data <- apply_cutoff(data, "frequency", lowerOther=2)

# Remove outliers
data <- remove_outliers(data, c(goal), id_col="WorkerId")

# Apply scaling
data <- data %>%
  dplyr::mutate(
    dplyr::across(
      dplyr::all_of(cols_to_scale),
      scaling_var,
      .names = "{.col}.s"
    )
  )
```

An now, let's check if an interaction term between length and frequency can help us. Here, we perform a quick test to check whether this might provide significant improvement of fit (assuming that our model adheres to the necessary assumptions...):

First a check for collinearity and multicollinearity:

```{r}
data$freqtimeslen.s <- data$frequency.s * data$length.s
preds <- data %>%
  dplyr::select(frequency.s, length.s, freqtimeslen.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + length.s + freqtimeslen.s, data)
vif(m)
```

```{r}
m0 <- lmer(GPT ~ frequency.s + length.s + (frequency.s + length.s + length.s*frequency.s | WorkerId) + (frequency.s + length.s + length.s*frequency.s | Text_ID),
  data=na.omit(data),
  REML=FALSE)
summary(m0)

m1 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + (frequency.s + length.s + length.s*frequency.s | WorkerId) + (frequency.s + length.s + length.s*frequency.s | Text_ID),
  data=na.omit(data),
  REML=FALSE)
summary(m1)

anova(m0, m1)
```

There is indication that we may want to reject the null hypothesis. Let's redraw the relevant plots.

```{r}
plot(fitted(m1), resid(m1))
abline(h = 0)

plot_bins(m1, "frequency.s", bins=25, data=data)
plot_bins(m1, "length.s", bins=25, data=data)

qqnorm(resid(m1))
qqline(resid(m1))
hist(resid(m1))

plot(data$frequency.s, resid(m1)); abline(h=0,lty=2)
plot(data$length.s, resid(m1)); abline(h=0,lty=2)
plot(data$freqtimeslen.s, resid(m1)); abline(h=0,lty=2)

re <- ranef(m1)
qqnorm(re$WorkerId[,1]); qqline(re$WorkerId[,1])
qqnorm(re$WorkerId[,2]); qqline(re$WorkerId[,2])
qqnorm(re$WorkerId[,3]); qqline(re$WorkerId[,3])
qqnorm(re$WorkerId[,4]); qqline(re$WorkerId[,4])
qqnorm(re$Text_ID[,1]); qqline(re$Text_ID[,1])
qqnorm(re$Text_ID[,2]); qqline(re$Text_ID[,2])
qqnorm(re$Text_ID[,3]); qqline(re$Text_ID[,3])
qqnorm(re$Text_ID[,4]); qqline(re$Text_ID[,4])
```

We do see an improvement for frequency where more bins land within the CI. Furthermore, the artifacts are gone.

```{r}
m <- lmer(log(GPT) ~ frequency.s + length.s + frequency.s*length.s + (frequency.s + length.s + length.s*frequency.s | WorkerId) + (frequency.s + length.s + length.s*frequency.s | Text_ID),
  data=na.omit(data),
  REML=FALSE)
summary(m1)
```

```{r}
plot(fitted(m), resid(m))
abline(h = 0)

plot_bins(m, "frequency.s", bins=50, data=data, response_transform="exp")
plot_bins(m, "length.s", bins=50, data=data, response_transform="exp")

qqnorm(resid(m))
qqline(resid(m))
hist(resid(m))

plot(data$frequency.s, resid(m1)); abline(h=0,lty=2)
plot(data$length.s, resid(m1)); abline(h=0,lty=2)

re <- ranef(m)
qqnorm(re$WorkerId[,1]); qqline(re$WorkerId[,1])
qqnorm(re$WorkerId[,2]); qqline(re$WorkerId[,2])
qqnorm(re$WorkerId[,3]); qqline(re$WorkerId[,3])
qqnorm(re$WorkerId[,4]); qqline(re$WorkerId[,4])
qqnorm(re$Text_ID[,1]); qqline(re$Text_ID[,1])
qqnorm(re$Text_ID[,2]); qqline(re$Text_ID[,2])
qqnorm(re$Text_ID[,3]); qqline(re$Text_ID[,3])
qqnorm(re$Text_ID[,4]); qqline(re$Text_ID[,4])
```

The Q-Q plot looks better. However, the relationship between frequency and GPT does not seem to have improved.

Any other transformation has severe implications for interpretability. Even the log-model is problematic since it contradicts prior knowledge about the linearity of these effects, especially of surprisal that we add later.

Maybe the normality of residuals can be improved by including spillover?

#### Inclusion of spillover

The method for spillover inclusion may be a bit problematic if our model does not adhere to the normality of residuals assumption. We do have a high number of data points which may be sufficient to yield reliable tests nonetheless. Furthermore, the inclusion of insignificant spillover terms will not inflate Type I errors for our candidate predictors.

##### Spillover 1

```{r}
data_spill1 <- add_lags_scaled(
  data,
  lag_cols = c("frequency", "length", "surprisal"),
  group_cols = c("WorkerId", "Text_ID"),
  n_lags = 1
)

data_spill1 <- data_spill1 %>%
  dplyr::mutate(
    dplyr::across(
      dplyr::all_of(c("surprisal1", "length1", "frequency1")),
      scaling_var,
      .names = "{.col}.s"
    )
  )

data_spill1$freqlen.s <- data_spill1$frequency.s * data_spill1$length.s
data_spill1$freqlen1.s <- data_spill1$frequency1.s * data_spill1$length1.s
preds <- na.omit(data_spill1) %>%
  dplyr::select(frequency.s, length.s, frequency1.s, length1.s, freqlen.s, freqlen1.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s, data_spill1)
vif(m)
```

Good.

```{r}
m0 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + length1.s*frequency1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + length1.s*frequency1.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0)

m1 <- lmer(GPT ~ frequency.s + frequency1.s + length.s + length1.s + frequency.s*length.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + length1.s*frequency1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + length1.s*frequency1.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1)

anova(m0, m1)
```

```{r}
rr <- rePCA(m0)
cc <- getME(m0, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:7], nm[1:7])
dimnames(rr$Text_ID[[2]]) <- list(nm[8:14], nm[8:14])
summary(rr)
```

Let's remove the random slopes for frequency1.s:length1.s because it does not explain any variance.

```{r}
m0 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0)

m1 <- lmer(GPT ~ frequency.s + frequency1.s + length.s + length1.s + frequency.s*length.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1)

anova(m0, m1)

```

Still singular...

```{r}
rr <- rePCA(m0)
cc <- getME(m0, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:6], nm[1:6])
dimnames(rr$Text_ID[[2]]) <- list(nm[7:12], nm[7:12])
summary(rr)
```

Okay, let's remove frequency.s:length.s from the WorkerId group:

```{r}
m0 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0)

m1 <- lmer(GPT ~ frequency.s + frequency1.s + length.s + length1.s + frequency.s*length.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1)

anova(m0, m1)
```

We can reject the null hypothesis.

Let's check the plots:

```{r}
plot(fitted(m1), resid(m1))
abline(h = 0)

plot_bins(m1, "frequency.s", bins=25, data=data_spill1)
plot_bins(m1, "frequency1.s", bins=25, data=data_spill1)
plot_bins(m1, "length.s", bins=25, data=data_spill1)
plot_bins(m1, "length1.s", bins=25, data=data_spill1)

qqnorm(resid(m1))
qqline(resid(m1))
hist(resid(m1))

plot(na.omit(data_spill1)$frequency.s, resid(m1)); abline(h=0,lty=2)
plot(na.omit(data_spill1)$length.s, resid(m1)); abline(h=0,lty=2)
plot(na.omit(data_spill1)$frequency1.s, resid(m1)); abline(h=0,lty=2)
plot(na.omit(data_spill1)$length1.s, resid(m1)); abline(h=0,lty=2)

re <- ranef(m1)
qqnorm(re$WorkerId[,1]); qqline(re$WorkerId[,1])
qqnorm(re$WorkerId[,2]); qqline(re$WorkerId[,2])
qqnorm(re$WorkerId[,3]); qqline(re$WorkerId[,3])
qqnorm(re$WorkerId[,4]); qqline(re$WorkerId[,4])
qqnorm(re$WorkerId[,5]); qqline(re$WorkerId[,5])
qqnorm(re$Text_ID[,1]); qqline(re$Text_ID[,1])
qqnorm(re$Text_ID[,2]); qqline(re$Text_ID[,2])
qqnorm(re$Text_ID[,3]); qqline(re$Text_ID[,3])
qqnorm(re$Text_ID[,4]); qqline(re$Text_ID[,4])
qqnorm(re$Text_ID[,5]); qqline(re$Text_ID[,5])
qqnorm(re$Text_ID[,6]); qqline(re$Text_ID[,6])
```

Nothing drastically changed with respect to our assumptions except for the normality of the random frequency residuals in the Text_ID group which exhibits a marked S-shape.

##### Spillover 2

```{r}
data_spill2 <- add_lags_scaled(
  data,
  lag_cols = c("frequency", "length", "surprisal"),
  group_cols = c("WorkerId", "Text_ID"),
  n_lags = 2
)

data_spill2 <- data_spill2 %>%
  dplyr::mutate(
    dplyr::across(
      dplyr::all_of(c("surprisal1", "length1", "frequency1", "surprisal2", "length2", "frequency2")),
      scaling_var,
      .names = "{.col}.s"
    )
  )

data_spill2$freqlen.s <- data_spill2$frequency.s * data_spill2$length.s
data_spill2$freqlen1.s <- data_spill2$frequency1.s * data_spill2$length1.s
data_spill2$freqlen2.s <- data_spill2$frequency2.s * data_spill2$length2.s
preds <- na.omit(data_spill2) %>%
  dplyr::select(frequency.s, frequency1.s, frequency2.s, length.s, length1.s, length2.s, freqlen.s, freqlen1.s, freqlen2.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + freqlen.s + freqlen1.s + freqlen2.s, data_spill2)
vif(m)
```

Unproblematic.

Now we only add spillover 2 variables where we added spillover 1 to prevent singularity issues:

```{r}
m0 <- lmer(GPT ~ frequency.s + frequency1.s + length.s + length1.s + frequency.s*length.s + frequency1.s*length1.s + (frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s | WorkerId) + (frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)
summary(m0)

m1 <- lmer(GPT ~ frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + frequency.s*length.s + frequency1.s*length1.s + frequency2.s*length2.s + (frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s | WorkerId) + (frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)
summary(m1)

anova(m0, m1)
```

```{r}
rr <- rePCA(m1)
cc <- getME(m1, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:7], nm[1:7])
dimnames(rr$Text_ID[[2]]) <- list(nm[8:15], nm[8:15])
summary(rr)
```

We need to remove length2.s random coefficient from WorkerId.

```{r}
m0 <- lmer(GPT ~ frequency.s + frequency1.s + length.s + length1.s + frequency.s*length.s + frequency1.s*length1.s + (frequency.s + frequency1.s + frequency2.s + length.s + length1.s | WorkerId) + (frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)
summary(m0)

m1 <- lmer(GPT ~ frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + frequency.s*length.s + frequency1.s*length1.s + frequency2.s*length2.s + (frequency.s + frequency1.s + frequency2.s + length.s + length1.s | WorkerId) + (frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)
summary(m1)

anova(m0, m1)

```

```{r}
rr <- rePCA(m0)
cc <- getME(m0, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:6], nm[1:6])
dimnames(rr$Text_ID[[2]]) <- list(nm[7:14], nm[7:14])
summary(rr)

rr <- rePCA(m1)
cc <- getME(m1, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:6], nm[1:6])
dimnames(rr$Text_ID[[2]]) <- list(nm[7:14], nm[7:14])
summary(rr)

```

Remove correlations between random coefficients for length.1s in WorkerId:

```{r}
m0 <- lmer(GPT ~ frequency.s + frequency1.s + length.s + length1.s + frequency.s*length.s + frequency1.s*length1.s + (frequency.s + length.s + frequency1.s + frequency2.s | WorkerId) + (frequency.s + length.s + length.s*frequency.s + frequency1.s + length1.s + frequency2.s + length2.s | Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)
summary(m0)

m1 <- lmer(GPT ~ frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + frequency.s*length.s + frequency1.s*length1.s + frequency2.s*length2.s + (frequency.s + length.s + frequency1.s + frequency2.s | WorkerId) + (frequency.s + length.s + length.s*frequency.s + frequency1.s + length1.s + frequency2.s + length2.s | Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)
summary(m1)

anova(m0, m1)

```

```{r}
rr <- rePCA(m0)
cc <- getME(m0, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:5], nm[1:5])
dimnames(rr$Text_ID[[2]]) <- list(nm[6:13], nm[6:13])
summary(rr)

rr <- rePCA(m1)
cc <- getME(m1, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:5], nm[1:5])
dimnames(rr$Text_ID[[2]]) <- list(nm[6:13], nm[6:13])
summary(rr)
```

Remove correlations for frequency2.s and frequency.s:length.s:

```{r}
m0 <- lmer(GPT ~ frequency.s + frequency1.s + length.s + length1.s + frequency.s*length.s + frequency1.s*length1.s + (frequency.s + length.s + frequency1.s | WorkerId) + (frequency2.s + 0 | WorkerId) + (frequency.s + length.s + frequency1.s + length1.s + frequency2.s + length2.s | Text_ID) + (length.s:frequency.s + 0 | Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)
summary(m0)

m1 <- lmer(GPT ~ frequency.s + frequency1.s + frequency2.s + length.s + length1.s + length2.s + frequency.s*length.s + frequency1.s*length1.s + frequency2.s*length2.s + (frequency.s + length.s + frequency1.s | WorkerId) + (frequency2.s + 0 | WorkerId) + (frequency.s + length.s + frequency1.s + length1.s + frequency2.s + length2.s | Text_ID) + (length.s:frequency.s + 0 | Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)
summary(m1)

anova(m0, m1)

```

We cannot reject the null-hypothesis. Thus, we settle with the spillover-1 model:

```{r}
m_split1 <- lmer(GPT ~ frequency.s + frequency1.s + length.s + length1.s + frequency.s*length.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
```

#### Analysis of surprisal

```{r}
preds <- na.omit(data_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, surprisal.s, surprisal1.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + surprisal.s + surprisal1.s, na.omit(data_spill1))
vif(m)
```

```{r}
hist(data_spill1$surprisal)
```

```{r}
m0_surpr <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + length1.s + frequency1.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s + surprisal.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_surpr)

m1_surpr <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s + surprisal.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_surpr)

anova(m0_surpr, m1_surpr)
```

```{r}
rr <- rePCA(m0_surpr)
cc <- getME(m0_surpr, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:6], nm[1:6])
dimnames(rr$Text_ID[[2]]) <- list(nm[7:13], nm[7:13])
summary(rr)

rr <- rePCA(m1_surpr)
cc <- getME(m1_surpr, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:6], nm[1:6])
dimnames(rr$Text_ID[[2]]) <- list(nm[7:13], nm[7:13])
summary(rr)
```

```{r}
m0_surpr <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + length1.s + frequency1.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (0 + surprisal.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_surpr)

m1_surpr <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (0 + surprisal.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_surpr)

anova(m0_surpr, m1_surpr)
```

We can reject the null hypothesis that surprisal is not predictive. Let's check spillover effects:

##### Spillover 1

```{r}
m0_surpr_spill1 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (0 + surprisal.s + surprisal1.s || WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_surpr_spill1)

m1_surpr_spill1 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (0 + surprisal.s + surprisal1.s || WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_surpr_spill1)

anova(m0_surpr_spill1, m1_surpr_spill1)
```

```{r}
rr <- rePCA(m0_surpr_spill1)
cc <- getME(m0_surpr_spill1, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:7], nm[1:7])
dimnames(rr$Text_ID[[2]]) <- list(nm[8:15], nm[8:15])
summary(rr)

rr <- rePCA(m1_surpr_spill1)
cc <- getME(m1_surpr_spill1, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:7], nm[1:7])
dimnames(rr$Text_ID[[2]]) <- list(nm[8:15], nm[8:15])
summary(rr)
```

marker

```{r}
m0_surpr_spill1 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_surpr_spill1)

m1_surpr_spill1 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_surpr_spill1)

anova(m0_surpr_spill1, m1_surpr_spill1)
```

```{r}
rr <- rePCA(m0_surpr_spill1)
cc <- getME(m0_surpr_spill1, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:5], nm[1:5])
dimnames(rr$Text_ID[[2]]) <- list(nm[6:13], nm[6:13])
summary(rr)

rr <- rePCA(m1_surpr_spill1)
cc <- getME(m1_surpr_spill1, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:5], nm[1:5])
dimnames(rr$Text_ID[[2]]) <- list(nm[6:13], nm[6:13])
summary(rr)
```

marker2

```{r}
m0_surpr_spill1 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + (frequency.s + frequency1.s + length.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_surpr_spill1)

m1_surpr_spill1 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_surpr_spill1)

anova(m0_surpr_spill1, m1_surpr_spill1)
```

This tells us that we should include surprisal spillover 1. What about spillover 2?

##### Spillover 2

```{r}
preds <- na.omit(data_spill2) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, surprisal.s, surprisal1.s, surprisal2.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + surprisal.s + surprisal1.s + surprisal2.s, na.omit(data_spill2))
vif(m)
```

```{r}
m0_surpr_spill2 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + surprisal2.s| Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)

m1_surpr_spill2 <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + surprisal2.s + (frequency.s + frequency1.s + length.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + surprisal2.s| Text_ID),
  data=na.omit(data_spill2),
  REML=FALSE)

anova(m0_surpr_spill2, m1_surpr_spill2)
```

```{r}
summary(m0_surpr_spill2)
summary(m1_surpr_spill2)
```

Thus, we do not include spillover window 2 for surprisal.

```{r}
plot(fitted(m1_surpr_spill1), resid(m1_surpr_spill1))
abline(h = 0)

plot_bins(m1_surpr_spill1, "frequency.s", bins=25, data=data_spill1)
plot_bins(m1_surpr_spill1, "frequency1.s", bins=25, data=data_spill1)
plot_bins(m1_surpr_spill1, "length.s", bins=25, data=data_spill1)
plot_bins(m1_surpr_spill1, "length1.s", bins=25, data=data_spill1)
plot_bins(m1_surpr_spill1, "surprisal.s", bins=25, data=data_spill1)
plot_bins(m1_surpr_spill1, "surprisal1.s", bins=25, data=data_spill1)

qqnorm(resid(m1_surpr_spill1))
qqline(resid(m1_surpr_spill1))
hist(resid(m1_surpr_spill1))

plot(na.omit(data_spill1)$frequency.s, resid(m1_surpr_spill1)); abline(h=0,lty=2)
plot(na.omit(data_spill1)$length.s, resid(m1_surpr_spill1)); abline(h=0,lty=2)
plot(na.omit(data_spill1)$frequency1.s, resid(m1_surpr_spill1)); abline(h=0,lty=2)
plot(na.omit(data_spill1)$length1.s, resid(m1_surpr_spill1)); abline(h=0,lty=2)

re <- ranef(m1)
qqnorm(re$WorkerId[,1]); qqline(re$WorkerId[,1])
qqnorm(re$WorkerId[,2]); qqline(re$WorkerId[,2])
qqnorm(re$WorkerId[,3]); qqline(re$WorkerId[,3])
qqnorm(re$WorkerId[,4]); qqline(re$WorkerId[,4])
qqnorm(re$WorkerId[,5]); qqline(re$WorkerId[,5])
qqnorm(re$Text_ID[,1]); qqline(re$Text_ID[,1])
qqnorm(re$Text_ID[,2]); qqline(re$Text_ID[,2])
qqnorm(re$Text_ID[,3]); qqline(re$Text_ID[,3])
qqnorm(re$Text_ID[,4]); qqline(re$Text_ID[,4])
qqnorm(re$Text_ID[,5]); qqline(re$Text_ID[,5])
qqnorm(re$Text_ID[,6]); qqline(re$Text_ID[,6])
qqnorm(re$Text_ID[,7]); qqline(re$Text_ID[,7])
qqnorm(re$Text_ID[,8]); qqline(re$Text_ID[,8])
```

#### Analysis of candidates

Now that we have decided on a model, we start testing the candidates. In each case, we will first do some data inspection and then we perform the statistical test.

##### unweighted local

TODO: recompute all of these.

```{r}
load_data <- function(data_dir, spill=0){
  data <- read.csv(data_dir)
  
  # Get names of numeric columns
  numeric_cols <- names(data)[sapply(data, is.numeric)]
  # Subset to numeric columns you want to scale
  excluded_vars <- c(goal, "WorkerId", "item", "element", "Text_ID", "zone", "chunksentence")
  cols_to_scale <- setdiff(numeric_cols, excluded_vars)
  
  # Apply cut-off
  # Provo already comes with a minimal value of 81 for GPT
  data <- apply_cutoff(data, goal)
  data <- apply_cutoff(data, "frequency", lowerOther=2)
  
  # Remove outliers
  data <- remove_outliers(data, c(goal), id_col="WorkerId")
  
  # Add spillover
  data <- add_lags_scaled(
    data,
    lag_cols = cols_to_scale,
    group_cols = c("WorkerId", "Text_ID"),
    n_lags = spill
  )
  
  # Apply scaling
  data <- data %>% dplyr::mutate(
    dplyr::across(
      dplyr::all_of(cols_to_scale),
      scaling_var,
      .names = "{.col}.s"
    )
  )
  
  # Apply scaling for spillover columns
  if (spill > 0) {
    data <- data %>%
    dplyr::mutate(
      dplyr::across(
        dplyr::all_of(unlist(lapply(seq_len(spill), function(i) paste0(cols_to_scale, i)))),
        scaling_var,
        .names = "{.col}.s"
      )
    )
  }
  data
}
data_spill1 <- load_data(data_dir, spill=1)
data_spill1$freqlen.s <- data_spill1$frequency.s*data_spill1$length.s
data_spill1$freqlen1.s <- data_spill1$frequency1.s*data_spill1$length1.s
```

###### Attention entropy

```{r}
hist(data_spill1$attention_entropy)
```

This is problematic. The first word in each sentence receives attention entropy of 0 (pathological case; nothing in the memory to attend to). The second word also receives 0 since it attennds 100 % to the only word in memory. We remove these two cases of a proper analysis of the cases where we have a proper theoretical motivation.

```{r}
data_spill1 <- apply_cutoff(data_spill1, "attention_entropy", lowerOther=0)

hist(data_spill1$attention_entropy)
```

Now, let's check collinearity and multicollinearity:

```{r}
preds <- na.omit(data_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, attention_entropy.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + attention_entropy.s, na.omit(data_spill1))
vif(m)
```

We only test the candidate without spillover. We multiply the p-value by the number of evaluations (16) (Bonferroni).

```{r}
m0_entr_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_entropy.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_entropy.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_entr_ul)

m1_entr_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_entropy.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_entropy.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_entropy.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_entr_ul)

anova_entr_ul <- anova(m0_entr_ul, m1_entr_ul)
anova_entr_ul
```

```{r}
anova_bonf <- function(m0, m1, num = 16) {
  a <- anova(m0, m1)          # keep the anova object
  tab <- as.data.frame(a)     # we'll format ourselves for printing

  # Compute adjusted p for the comparison row (row 2)
  p_raw <- tab$`Pr(>Chisq)`[2]
  p_bonf <- if (is.na(p_raw)) NA_real_ else min(p_raw * num, 1)

  # Add columns (blank on row 1 to mimic anova)
  tab$`Pr(>Chisq)_bonf` <- c(NA, p_bonf)

  # Stars exactly like anova's legend
  stars <- function(p) {
    if (is.na(p)) "" else if (p < 0.001) "***"
    else if (p < 0.01) "**"
    else if (p < 0.05) "*"
    else if (p < 0.1) "."
    else ""
  }
  tab$` ` <- c("", stars(p_bonf))  # unlabeled col like anova's trailing star column

  # ---- Printing: mimic anova formatting ----
  # Turn off scientific notation
  op <- options(scipen = 999)
  on.exit(options(op), add = TRUE)

  # Format key columns to look like anova output
  fmt_int <- function(x) ifelse(is.na(x), "", formatC(x, format = "f", digits = 0))
  fmt_num <- function(x, d) ifelse(is.na(x), "", formatC(x, format = "f", digits = d))
  fmt_p   <- function(x) ifelse(is.na(x), "", format.pval(x, digits = 4, eps = 1e-16))

  out <- tab
  # anova prints these without decimals:
  out$npar      <- fmt_int(out$npar)
  out$AIC       <- fmt_int(out$AIC)
  out$BIC       <- fmt_int(out$BIC)
  out$logLik    <- fmt_int(out$logLik)
  out$`-2*log(L)`<- fmt_int(out$`-2*log(L)`)

  # these with a few decimals:
  out$Chisq     <- fmt_num(out$Chisq, 3)
  out$Df        <- fmt_int(out$Df)
  out$`Pr(>Chisq)`       <- fmt_p(as.numeric(tab$`Pr(>Chisq)`))
  out$`Pr(>Chisq)_bonf`  <- fmt_p(as.numeric(tab$`Pr(>Chisq)_bonf`))

  # Print with rownames and spacing like anova
  print(out, quote = FALSE, right = TRUE, row.names = TRUE)
  cat("---\n")
  cat("Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1\n")

  invisible(list(anova = a, table = tab, p_bonf = p_bonf))
}

anova_bonf(m0_entr_ul, m1_entr_ul, 16)
```

```{r}
source("utils.R")
make_plots <- function(model, candidate, data, random1=5, random2=8) {
  plot(fitted(model), resid(model))
  abline(h = 0)
  
  plot_bins(model, "frequency.s", bins=25, data=data)
  plot_bins(model, "frequency1.s", bins=25, data=data)
  plot_bins(model, "length.s", bins=25, data=data)
  plot_bins(model, "length1.s", bins=25, data=data)
  plot_bins(model, "surprisal.s", bins=25, data=data)
  plot_bins(model, "surprisal1.s", bins=25, data=data)
  plot_bins(model, candidate, bins=25, data=data)
  
  qqnorm(resid(model))
  qqline(resid(model))
  hist(resid(model))
  
  plot(na.omit(data)$frequency.s, resid(model)); abline(h=0,lty=2)
  plot(na.omit(data)$length.s, resid(model)); abline(h=0,lty=2)
  plot(na.omit(data)$frequency1.s, resid(model)); abline(h=0,lty=2)
  plot(na.omit(data)$length1.s, resid(model)); abline(h=0,lty=2)
  plot(na.omit(data)[[candidate]], resid(model)); abline(h=0,lty=2)
  
  re <- ranef(m1)
  for (x in 1:random1) {
    qqnorm(re$WorkerId[,x]); qqline(re$WorkerId[,x])
  }
  for (x in 1:random2) {
    qqnorm(re$Text_ID[,x]); qqline(re$Text_ID[,x])
  }
}
make_plots(m1_entr_ul, "attention_entropy.s", data_spill1)
```

###### Attention distance

```{r}
data_spill1 <- load_data(data_dir, spill=1)
data_spill1$freqlen.s <- data_spill1$frequency.s*data_spill1$length.s
data_spill1$freqlen1.s <- data_spill1$frequency1.s*data_spill1$length1.s

hist(data_spill1$attention_distance)
```

We don't see any irregularities.

Let's check collinearity and multicollinearity:

```{r}
preds <- na.omit(data_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, attention_distance.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + attention_distance.s, na.omit(data_spill1))
vif(m)
```

```{r}
m0_dist_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_distance.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_distance.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_dist_ul)

m1_dist_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_distance.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_distance.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_distance.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_dist_ul)

anova_bonf(m0_dist_ul, m1_dist_ul)
```

We have a singular fit.

```{r}
rr <- rePCA(m0_dist_ul)
cc <- getME(m0_dist_ul, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:6], nm[1:6])
dimnames(rr$Text_ID[[2]]) <- list(nm[7:15], nm[7:15])
summary(rr)

rr <- rePCA(m1_dist_ul)
cc <- getME(m1_dist_ul, "cnms")
nm <- unlist(cc)
dimnames(rr$WorkerId[[2]]) <- list(nm[1:6], nm[1:6])
dimnames(rr$Text_ID[[2]]) <- list(nm[7:15], nm[7:15])
summary(rr)
```

Remove length1.s from WorkerId.

```{r}
m0_dist_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_distance.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_distance.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_dist_ul)

m1_dist_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_distance.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_distance.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_distance.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_dist_ul)

anova_bonf(m0_dist_ul, m1_dist_ul)
```

```{r}
make_plots(m1_dist_ul, "attention_distance.s", data_spill1)
```

###### Attention activation

```{r}
data_spill1 <- load_data(data_dir, spill=1)
data_spill1$freqlen.s <- data_spill1$frequency.s*data_spill1$length.s
data_spill1$freqlen1.s <- data_spill1$frequency1.s*data_spill1$length1.s

hist(data_spill1$attention_activation)
```

We have a lot of 0 values. Let's discard the very first word since it is a special case.

```{r}
data_spill1 <- apply_cutoff(data_spill1, "position", lowerOther=1)
hist(data_spill1$attention_activation)
```

```{r}
preds <- na.omit(data_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, attention_activation.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + attention_activation.s, na.omit(data_spill1))
vif(m)
```

```{r}
m0_act_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_activation.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_activation.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_dist_ul)

m1_act_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_activation.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_activation.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_activation.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_dist_ul)

anova_bonf(m0_dist_ul, m1_dist_ul)
```

```{r}
make_plots(m1_act_ul, "attention_activation.s", data_spill1)
```

###### Attention difference

```{r}
data_spill1 <- load_data(data_dir, spill=1)
data_spill1$freqlen.s <- data_spill1$frequency.s*data_spill1$length.s
data_spill1$freqlen1.s <- data_spill1$frequency1.s*data_spill1$length1.s

hist(data_spill1$attention_difference)
```

```{r}
preds <- na.omit(data_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, attention_difference.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + attention_difference.s, na.omit(data_spill1))
vif(m)
```

```{r}
m0_diff_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_difference.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_difference.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_diff_ul)

m1_diff_ul <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_difference.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_difference.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_difference.s | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m1_diff_ul)

anova_bonf(m0_diff_ul, m1_diff_ul)
```

```{r}
make_plots(m1_diff_ul, "attention_difference.s", data_spill1)
```

##### unweighted global

###### Attention entropy

```{r}
data_dir_ug <- "../data/provo_RT_test_preprocessed_exp1_4_0_ug.csv"
data_ug_spill1 <- load_data(data_dir_ug, spill=1)
data_ug_spill1$freqlen.s <- data_ug_spill1$frequency.s*data_ug_spill1$length.s
data_ug_spill1$freqlen1.s <- data_ug_spill1$frequency1.s*data_ug_spill1$length1.s

hist(data_ug_spill1$attention_entropy, n=20)
data_ug_spill1 <- apply_cutoff(data_ug_spill1, "attention_entropy", lowerOther=0)
hist(data_ug_spill1$attention_entropy, n=20)
```

The are some peculiarities in the left area of the histogram that we cannot explain.

```{r}
preds <- na.omit(data_ug_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, attention_entropy.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + attention_entropy.s, na.omit(data_ug_spill1))
vif(m)
```

```{r}
m0_entr_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_entropy.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_entropy.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m0_entr_ug)

m1_entr_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_entropy.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_entropy.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_entropy.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m1_entr_ug)

anova_bonf(m0_entr_ug, m1_entr_ug)
```

```{r}
make_plots(m1_entr_ug, "attention_entropy.s", data_ug_spill1)
```

###### Attention distance

```{r}
data_ug_spill1 <- load_data(data_dir_ug, spill=1)
data_ug_spill1$freqlen.s <- data_ug_spill1$frequency.s*data_ug_spill1$length.s
data_ug_spill1$freqlen1.s <- data_ug_spill1$frequency1.s*data_ug_spill1$length1.s

hist(data_ug_spill1$attention_distance, n=20)
```

```{r}
preds <- na.omit(data_ug_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, attention_distance.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + attention_distance.s, na.omit(data_ug_spill1))
vif(m)
```

```{r}
m0_dist_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_distance.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_distance.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m0_dist_ug)

m1_dist_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_distance.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_distance.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_distance.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m1_dist_ug)

anova_bonf(m0_dist_ug, m1_dist_ug)
```

```{r}
rr <- rePCA(m0_dist_ug)
cc <- getME(m0_dist_ug, "cnms")
nm <- unlist(cc)

l1 <- nrow(rr$WorkerId[[2]])
l2 <- nrow(rr$Text_ID[[2]])
dimnames(rr$WorkerId[[2]]) <- list(nm[1:l1], nm[1:l1])
dimnames(rr$Text_ID[[2]]) <- list(nm[(l1+1):(l1+l2)], nm[(l1+1):(l1+l2)])
summary(rr)

rr <- rePCA(m1_dist_ug)
cc <- getME(m1_dist_ug, "cnms")
nm <- unlist(cc)

l1 <- nrow(rr$WorkerId[[2]])
l2 <- nrow(rr$Text_ID[[2]])
dimnames(rr$WorkerId[[2]]) <- list(nm[1:l1], nm[1:l1])
dimnames(rr$Text_ID[[2]]) <- list(nm[(l1+1):(l1+l2)], nm[(l1+1):(l1+l2)])
summary(rr)
```

Remove correlations for frequency.s:length.s in TextID:

```{r}
m0_dist_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_distance.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + surprisal.s + surprisal1.s + attention_distance.s | Text_ID) + (0 + length.s:frequency.s || Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m0_dist_ug)

m1_dist_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_distance.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_distance.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + surprisal.s + surprisal1.s + attention_distance.s | Text_ID) + (0 + length.s:frequency.s || Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m1_dist_ug)

anova_bonf(m0_dist_ug, m1_dist_ug)
```

```{r}
make_plots(m1_dist_ug, "attention_distance.s", data_ug_spill1)
```

###### Attention activation

```{r}
data_ug_spill1 <- load_data(data_dir_ug, spill=1)
data_ug_spill1$freqlen.s <- data_ug_spill1$frequency.s*data_ug_spill1$length.s
data_ug_spill1$freqlen1.s <- data_ug_spill1$frequency1.s*data_ug_spill1$length1.s

hist(data_ug_spill1$attention_activation)
data_ug_spill1 <- apply_cutoff(data_ug_spill1, "position", lowerOther=1)
hist(data_ug_spill1$attention_activation)
```

```{r}
m0_act_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_activation.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_activation.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m0_act_ug)

m1_act_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_activation.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_activation.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_activation.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m1_act_ug)

anova_bonf(m0_act_ug, m1_act_ug)
```

```{r}
make_plots(m1_act_ug, "attention_activation.s", data_ug_spill1)
```

###### Attention difference

```{r}
data_ug_spill1 <- load_data(data_dir_ug, spill=1)
data_ug_spill1$freqlen.s <- data_ug_spill1$frequency.s*data_ug_spill1$length.s
data_ug_spill1$freqlen1.s <- data_ug_spill1$frequency1.s*data_ug_spill1$length1.s

hist(data_ug_spill1$attention_difference)
```

```{r}
preds <- na.omit(data_ug_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, attention_difference.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + attention_difference.s, na.omit(data_ug_spill1))
vif(m)
```

```{r}
m0_diff_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_difference.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_difference.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m0_diff_ug)

m1_diff_ug <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_difference.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_difference.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_difference.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m1_diff_ug)

anova_bonf(m0_diff_ug, m1_diff_ug)
```

```{r}
make_plots(m1_diff_ug, "attention_difference.s", data_ug_spill1)
```

##### weighted local

###### Attention entropy

```{r}
data_dir_wl <- "../data/provo_RT_test_preprocessed_exp1_4_0_wl.csv"
data_wl_spill1 <- load_data(data_dir_wl, spill=1)
data_wl_spill1$freqlen.s <- data_wl_spill1$frequency.s*data_wl_spill1$length.s
data_wl_spill1$freqlen1.s <- data_wl_spill1$frequency1.s*data_wl_spill1$length1.s

hist(data_wl_spill1$attention_entropy, n=20)
```

```{r}
preds <- na.omit(data_wl_spill1) %>%
  dplyr::select(frequency.s, frequency1.s, length.s, length1.s, freqlen.s, freqlen1.s, attention_entropy.s)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency.s + frequency1.s + length.s + length1.s + freqlen.s + freqlen1.s + attention_entropy.s, na.omit(data_wl_spill1))
vif(m)
```

```{r}
m0_entr_wl <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_entropy.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_entropy.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m0_entr_wl)

m1_entr_wl <- lmer(GPT ~ frequency.s + length.s + frequency.s*length.s + surprisal.s + attention_entropy.s + length1.s + frequency1.s + frequency1.s*length1.s + surprisal1.s + (frequency.s + frequency1.s + length.s + attention_entropy.s | WorkerId) + (0 + length1.s | WorkerId) + (frequency.s + frequency1.s + length.s + length1.s + length.s*frequency.s + surprisal.s + surprisal1.s + attention_entropy.s | Text_ID),
  data=na.omit(data_ug_spill1),
  REML=FALSE)
summary(m1_entr_ug)

anova_bonf(m0_entr_ug, m1_entr_wl)
```

#### Power simulation for other corpora

------------------------------------------------------------------------

```{r}
library(simr)
power_interaction <- powerSim(
  m,
  test = fixed("frequency:length", method = "lr"),
  nsim = 200  # increase to 1000+ for a stable estimate
)
power_interaction

```

```{r}
workers_keep <- sample(unique(data$WorkerId), 10)
textid_keep <- sample(unique(data$Text_ID), 10)

data_10 <- subset(data, WorkerId %in% workers_keep)
data_10 <- subset(data_10, Text_ID %in% textid_keep)

m_simpler <- lmer(
  GPT ~ frequency + length + surprisal + 
    (1 + frequency + length + surprisal || WorkerId) +
    (1 + frequency + length + surprisal || Text_ID),
  data = na.omit(data_10),
  REML = FALSE
)
fixef(m_simpler)["surprisal"] <- 5

power_interaction <- powerSim(
  m_simpler,
  test = fixed("surprisal", method = "lr"),
  nsim = 100  # increase to 1000+ for a stable estimate
)
power_interaction

```

```{r}
m_simpler
```

```{r}
testUniformity(sim)
testDispersion(sim)
plotResiduals(sim, mf[["frequency"]])
plotResiduals(sim, mf[["surprisal"]])

```

\

```{r}
hist(data$logfreq)
hist(data$frequency)
```

##### Random effects normality

```{r}

re <- ranef(m)
qqnorm(re$WorkerId[,1]); qqline(re$WorkerId[,1])
qqnorm(re$WorkerId[,2]); qqline(re$WorkerId[,2])
qqnorm(re$WorkerId[,3]); qqline(re$WorkerId[,3])
qqnorm(re$WorkerId[,4]); qqline(re$WorkerId[,4])
qqnorm(re$Text_ID[,1]); qqline(re$Text_ID[,1])
qqnorm(re$Text_ID[,2]); qqline(re$Text_ID[,2])
qqnorm(re$Text_ID[,3]); qqline(re$Text_ID[,3])
qqnorm(re$Text_ID[,4]); qqline(re$Text_ID[,4])
```

TODO

##### Independent residuals

```{r}

acf(residuals(m))
```

MEANING?

##### \_\_\_

#### Inclusion of spillover

Let's try to determine the correct amount of spillover. We check this via a likelihood ratio test about the inclusion of spillover covariates:

```{r}
data$freqtimeslength <- data$frequency*data$length
data_spill1 <- add_lags_scaled(
  data,
  lag_cols = c("frequency", "length", "surprisal", "freqtimeslength"),
  group_cols = c("WorkerId", "Text_ID"),
  n_lags = 1
)
preds <- na.omit(data_spill1) %>%
  dplyr::select(frequency, length, freqtimeslength, frequency1, length1, freqtimeslength1)
cor_mat <- cor(preds)
round(cor_mat, 2)

m <- lm(GPT ~ frequency + frequency1 + length + length1 + freqtimeslength + freqtimeslength1, data_spill1)
vif(m)
```

```{r}
m0_spill1 <- lmer(GPT ~ frequency + length + frequency*length + (frequency + frequency1 + length + length1 + frequency*length + frequency1*length1 | WorkerId) + (frequency + frequency1 + length + length1 + frequency*length + frequency1*length1 | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
m0_spill1
```

We encountered a singularity. Let's remove random slopes for the interaction:

```{r}
m0_spill1 <- lmer(GPT ~ frequency + length + frequency*length + (frequency + frequency1 + length + length1 + frequency*length | WorkerId) + (frequency + frequency1 + length + length1 + frequency*length | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_spill1)
```

```{r}
m0_spill1 <- lmer(GPT ~ frequency + length + frequency*length + (frequency + frequency1 + length + frequency*length | WorkerId) + (frequency + frequency1 + length + length1 + frequency*length | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
summary(m0_spill1)
```

```{r}
m1_spill1 <- lmer(log(GPT) ~ frequency + frequency1 + length + length1 + (frequency + frequency1 + length + length1 | WorkerId) + (frequency + length | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
m1_spill1
```

Again, we have a convergence problem. The effect of frequency1 is very small. Let's try without it:

```{r}
m0_spill1 <- lmer(log(GPT) ~ frequency + length + (frequency + length + length1 | WorkerId) + (frequency + length + length1 | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
m0_spill1
```

```{r}
m1_spill1 <- lmer(log(GPT) ~ frequency + length + length1 + (frequency + length + length1 | WorkerId) + (frequency + length + length1 | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
m1_spill1
```

```{r}
anova(m0_spill1, m1_spill1)
```

We cannot refute the null hypothesis. Therefore, we do not include spillover.

#### Surprisal analysis

Now, let's check whether surprisal significantly predicts RTs.

```{r}
m0 <- lmer(log(GPT) ~ frequency + length + (surprisal + frequency + length | WorkerId) + (surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m0
```

Let's adjust this a bit:

```{r}
m0 <- lmer(log(GPT) ~ frequency + length + (frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m0
```

```{r}
m1 <- lmer(log(GPT) ~ surprisal + frequency + length + (frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
```

```{r}
anova(m0, m1)
```

This is evidence against the null-hypothesis of no effect based on surprisal (as expected). Let's check for spillover-effects of only surprisal:

```{r}
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (frequency + length | WorkerId) + (surprisal + surprisal1 + 0 || WorkerId) + (surprisal + surprisal1 + frequency + length | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
m0
```

```{r}
m1 <- lmer(log(GPT) ~ surprisal + surprisal1 + frequency + length + (frequency + length | WorkerId) + (surprisal + surprisal1 + 0 || WorkerId) + (surprisal + surprisal1 + frequency + length | Text_ID),
  data=na.omit(data_spill1),
  REML=FALSE)
m1
```

```{r}
anova(m0, m1)
```

We cannot reject the null hypothesis about surprisal spillover.

```{r}
m <- lmer(log(GPT) ~ surprisal + frequency + length + (frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
```

```{r}
qqnorm(resid(m)); qqline(resid(m))
hist(resid(m), breaks=30)
```

#### Analysis of candidates

Now that we have decided on a model, we start testing the candidates.

##### unweighted-unglobal

```{r}
load_data <- function(data_dir){
  data <- read.csv(data_dir)
  
  # Get names of numeric columns
  numeric_cols <- names(data)[sapply(data, is.numeric)]
  # Subset to numeric columns you want to scale
  excluded_vars <- c(goal, "WorkerId", "item", "element", "zone", "chunksentence")
  cols_to_scale <- setdiff(numeric_cols, excluded_vars)
  
  # Apply cut-off
  # Provo already comes with a minimal value of 81 for GPT
  data <- apply_cutoff(data, goal)
  data <- apply_cutoff(data, "frequency", lowerOther=2)
  
  # Remove outliers
  data <- remove_outliers(data, c(goal), id_col="WorkerId")
  
  # Apply scaling
  data <- data %>%
    mutate(across(all_of(cols_to_scale), scaling_var))
  data
}
```

```{r}
data <- load_data(data_dir)

preds <- data %>%
  dplyr::select(frequency, length, attention_entropy, attention_distance, attention_difference, attention_activation)
cor_mat <- cor(preds)
round(cor_mat, 2)
```

###### Attention entropy

```{r}
m <- lm(GPT ~ frequency + length + attention_entropy, data)
vif(m)

hist(data$attention_entropy)
# -> remove entries with lowest value since these are pathological cases (entropy = 0 for cases where no entropy can be computed due to zero items available in context or where only one item is available)

data <- apply_cutoff(data, "attention_entropy", lowerOther=min(data$attention_entropy), upperOther=Inf)
hist(data$attention_entropy)
```

```{r}
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(summary(m0))

m1 <- lmer(log(GPT) ~ attention_entropy + surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(summary(m1))

anova(m0, m1)
```

```{r}
plot_bins(m1, "attention_entropy", bins=25)
```

###### Attention distance

```{r}
data <- load_data(data_dir)
m <- lm(GPT ~ frequency + length + attention_distance, data)
vif(m)

hist(data$attention_distance)
```

```{r}
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(summary(m0))

m1 <- lmer(log(GPT) ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(summary(m1))

anova(m0, m1)
```

```{r}

# m1 <- lmer(GPT ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
#  data=na.omit(data),
#  REML=FALSE)
#print(summary(m1))

plot_bins(m1, "surprisal", "GPT", data, bins=25)
plot_bins(m1, "frequency", "GPT", data, bins=25)
```

```{r}

source("utils.R")
m1 <- lmer(log(GPT) ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(summary(m1))

plot_bins(m1, "surprisal", "GPT", data, bins=25)
plot_bins(m1, "frequency", "GPT", data, bins=25)
```

```{r}
x <- seq(min(data$surprisal), max(data$surprisal), length.out = 200)
eta <- fixef(m1)["(Intercept)"] + fixef(m1)["surprisal"] * x
y <- exp(eta)

plot(x, y, type = "l")


```

```{r}
data <- read.csv(data_dir)
  
data$logfreq <- log(data$frequency)
# Get names of numeric columns
numeric_cols <- names(data)[sapply(data, is.numeric)]
# Subset to numeric columns you want to scale
excluded_vars <- c(goal, "WorkerId", "item", "element", "zone", "chunksentence")
cols_to_scale <- setdiff(numeric_cols, excluded_vars)

# Apply cut-off
# Provo already comes with a minimal value of 81 for GPT
data <- apply_cutoff(data, goal)
data <- apply_cutoff(data, "frequency", lowerOther=2)

# Remove outliers
data <- remove_outliers(data, c(goal), id_col="WorkerId")

# Apply scaling
data <- data %>%
  mutate(across(all_of(cols_to_scale), scaling_var))

m1 <- lmer(log(GPT) ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m1
```

```{r}
plot_bins(m1, "length", bins=25)
plot_bins(m1, "logfreq", bins=25)
plot_bins(m1, "surprisal", bins=25)
plot_bins(m1, "attention_distance", bins=25)
```

```{r}
plot_bins(m1, "frequency", bins=25)
```

```{r}
m1 <- lmer(GPT ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
summary(m1)

source("utils.R")
plot_bins(m1, "frequency", bins=25, logy = FALSE)

sjPlot::plot_model(
    m1,
    type  = "pred",
    terms = c("frequency")
  )
```

###### TODO: find out why plot is linear –\> apparently nonlinear only for length but linear for surprisal (as predicted) and others.

###### TODO: find way to rescale x axis

###### \_\_\_\_\_

##### Attention entropy

###### unweighted-unglobal

```{r}
load_data <- function(data_dir){
  data <- read.csv(data_dir)
  
  # Get names of numeric columns
  numeric_cols <- names(data)[sapply(data, is.numeric)]
  # Subset to numeric columns you want to scale
  excluded_vars <- c(goal, "WorkerId", "item", "element", "zone", "chunksentence")
  cols_to_scale <- setdiff(numeric_cols, excluded_vars)
  
  # Apply cut-off
  # Provo already comes with a minimal value of 81 for GPT
  data <- apply_cutoff(data, goal)
  data <- apply_cutoff(data, "frequency", lowerOther=2)
  
  # Remove outliers
  data <- remove_outliers(data, c(goal), id_col="WorkerId")
  
  # Apply scaling
  data <- data %>%
    mutate(across(all_of(cols_to_scale), scaling_var))
  data
}
data <- load_data(data_dir)

m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m0
```

```{r}

m1 <- lmer(log(GPT) ~ attention_entropy + surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m1
```

```{r}
anova(m0, m1)
```

No positive result.

###### unweighted-global

```{r}

data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m0
```

```{r}
m1 <- lmer(log(GPT) ~ attention_entropy + surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m1
```

```{r}
anova(m0, m1)
```

No positive result.

###### weighted-unglobal

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m0
```

```{r}
m1 <- lmer(log(GPT) ~ attention_entropy + surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m1
```

```{r}
anova(m0, m1)
```

No positive result.

###### weighted-global

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m0
```

```{r}
m1 <- lmer(log(GPT) ~ attention_entropy + surprisal + frequency + length + (attention_entropy + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_entropy + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
m1
```

```{r}
anova(m0, m1)
```

```{r}
p <- sjPlot::plot_model(
    m1,
    type  = "pred",
    terms = "attention_entropy",
    show.data = TRUE,
  )
p
```

```{r}
hist(data$attention_entropy)
```

Based on this result, we have reason to reject the null hypothesis. However, are repeated testing scheme on the same data should make us cautious. The more frequent the tests, the higher the probability that find a false positive in at least one of the cases. The results on the other datasets will strengthen the robustness of this analysis.

##### Attention distance

###### unweighted-unglobal

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

###### unweighted-global

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

###### weighted-unglobal

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

###### weighted-global

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_distance + surprisal + frequency + length + (attention_distance + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_distance + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

Negative

##### Attention difference

###### unweighted-unglobal

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_difference + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_difference + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_difference + surprisal + frequency + length + (attention_difference + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_difference + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

###### unweighted-global

```{r}

data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_difference + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_difference + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_difference + surprisal + frequency + length + (attention_difference + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_difference + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

###### weighted-unglobal

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_difference + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_difference + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_difference + surprisal + frequency + length + (attention_difference + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_difference + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

Great! TODO

###### weighted-global

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_difference + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_difference + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_difference + surprisal + frequency + length + (attention_difference + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_difference + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

GREAT

##### Attention activation

###### unweighted-unglobal

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_activation + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_activation + surprisal + frequency + length + (attention_activation + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

This led to singularity issue. Let's remove the correlation term for the attention_activation random slope:

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (frequency + length | WorkerId) + (attention_activation + 0 | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_activation + surprisal + frequency + length + (frequency + length | WorkerId) + (attention_activation + 0 | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

###### unweighted-global

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_activation + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_activation + surprisal + frequency + length + (attention_activation + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

Singular fit... Let's try again:

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (frequency + length | WorkerId) + (attention_activation + 0 | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_activation + surprisal + frequency + length + (frequency + length | WorkerId) + (attention_activation + 0 | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

###### weighted-unglobal

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_activation + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_activation + surprisal + frequency + length + (attention_activation + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

Great. TODO

###### weighted-global

```{r}
data <- load_data(data_dir)
m0 <- lmer(log(GPT) ~ surprisal + frequency + length + (attention_activation + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m0)

m1 <- lmer(log(GPT) ~ attention_activation + surprisal + frequency + length + (attention_activation + frequency + length | WorkerId) + (surprisal + 0 | WorkerId) + (attention_activation + surprisal + frequency + length | Text_ID),
  data=na.omit(data),
  REML=FALSE)
print(m1)

anova(m0, m1)
```

GREAT

```{r}
plot_bins(m1, "attention_activation", bins=50)
```

```{r}
plot_model(
  m1,
  type = "pred",
  terms = "attention_activation",
  show.data = TRUE
  )
```

#### Without surprisal?

Possibly the candidates checked here explain surprisal (TODO). We check this:
