#### Imports

```{r}
library(Rmisc)
library(tidyverse)
library(stringr)
library(scales)
library(grid)
library(ggpubr)
library(MASS)
library(lme4)
library(stats)
library(modelr)
library(plotrix)
library(mgcv)
library(hexbin)
library(formattable)
library(MuMIn)
library(ggrepel)
library(data.table)
library(comprehenr)
library(ggplot2)
library(dplyr)
library(car)

source("utils.R")
```

#### Definitions

```{r}
data_dir <- "../data/provo_RT_test_preprocessed_exp1_4_0.csv"
goal <- "GPT"

candidates <- c("surprisal", "attention_entropy")
baseline_predictors <- c("frequency", "length", "position", "lemma", "element")
```

#### Data Preparation

```{r}

data <- read.csv(data_dir)

# Get names of numeric columns
numeric_cols <- names(data)[sapply(data, is.numeric)]
# Subset to numeric columns you want to scale
excluded_vars <- c(goal, "WorkerId", "item", "element", "zone", "chunksentence")

cols_to_scale <- setdiff(numeric_cols, excluded_vars)

# Apply cut-off
# Provo already comes with a minimal value of 81 for GPT
data <- apply_cutoff(data, goal)

# Remove outliers
data <- remove_outliers(data, c(goal), id_col="WorkerId")

# Apply scaling
data <- data %>%
  mutate(across(all_of(cols_to_scale), scaling_var))
```

For eye-tracking, we remove skipped-over words as they do not inform us about comprehension process durations.

#### Simple check of aggregated correlation

```{r}
compute_mean <- function(datasets, factor1, factor2) {
  formula_str <- paste("cbind(", factor1, ",", factor2, ") ~ item + zone")
  means <- aggregate(as.formula(formula_str), data=data, FUN = mean, na.rm = TRUE)
  corr <- cor.test(means[[factor1]], means[[factor2]], method="pearson")
  corr
}

compute_mean(data, "GPT", "surprisal")
compute_mean(data, "GPT", "attention_entropy")
```

#### First check of assumptions

We check for collinearity and multicollinearity (?) of the variables:

##### Pairwise collinearity:

We check this via a correlation matrix:

```{r}

preds <- data %>%
  dplyr::select(frequency, length, position, Text_ID, Sentence_Number, Word_Number)
cor_mat <- cor(preds)
round(cor_mat, 2)
```

We may have a problem for frequency-length.

##### Multicollinearity:

We detect multicollinearity using VIF. Thresholds are motivated by: <https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/j.2041-210X.2009.00001.x>

TODO

```{r}
m <- lm(GPT ~ frequency + length + position + Text_ID + Sentence_Number + Word_Number, data)
vif(m)
```

There is cause to worry about Sentence_Number and Word_Number. Word_Number is almost 5; we will leave it out.

#### Baseline model

We should include predictors frequency and length. But what about position, text number and sentence number (nested inside text numer)? We perform a first preliminary test without random effects:

```{r}
#| cache = TRUE

m <- lm(GPT ~ frequency + length + position + Text_ID + Sentence_Number,
  data=na.omit(data))
m
```

The coefficient for Text_ID is very small. Let's check for significance:

```{r}
m0 <- lm(GPT ~ frequency + length + position + Sentence_Number,
  data=na.omit(data))
anova(m0, m)
```

We definitely cannot refute the null hypothesis. Thus, we will not include it.

Now, let's include random effects. We will use some tricks to speed up the fitting. First, for the invidual items:

```{r}
#| cache = TRUE

lmer(GPT ~ frequency + length + position + Sentence_Number + (frequency + length + position + Sentence_Number | element),
  data=na.omit(data),
  REML=FALSE,
  lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))
```

```{r}
#| cache = TRUE

lmer(GPT ~ frequency + length + position + Sentence_Number + (frequency + length + position + Sentence_Number | WorkerId) + (frequency + length + position + Sentence_Number | lemma) + (frequency + length + position + Sentence_Number | element),
  data=na.omit(data),
  REML=FALSE,
  lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))
```

The effect for position seems pretty small. For now, we leave it out and check if it is significant later.

We note a standard deviation for the random intercept in the lemma group and consequently NaN values in the lemma correlation matrix. Additionally, there is a correlation of -1 between the length and frequency random slopes in the lemma group. Next, we try the same model but without correlations for the lemma group.

```{r}
#| cache = TRUE

m <- lmer(GPT ~ frequency + length + (frequency + length | WorkerId + element) + (frequency + length || lemma),
  data=na.omit(data),
  REML=FALSE)
m
```

Now, let's remove the random intercept for lemma since it appears to be very close to aor at zero:

```{r}
#| cache = TRUE

m <- lmer(GPT ~ frequency + length + (frequency + length | WorkerId + element) + (0 + frequency + length || lemma),
  data=na.omit(data),
  REML=FALSE)
m
```

Great. Now, let's check if adding position back in provides a significant effect:

```{r}
#| cache = TRUE

m0 <- lmer(GPT ~ frequency + length + (position + frequency + length | WorkerId + element) + (0 + position + frequency + length || lemma),
  data=na.omit(data),
  REML=FALSE)
m0
```

The model cannot converge. We leave out the random coefficient for position in the WorkerId group.

```{r}
#| cache = TRUE

m0 <- lmer(GPT ~ frequency + length + (frequency + length | WorkerId + element) + (0 + position + frequency + length || lemma),
  data=na.omit(data),
  REML=FALSE)
m0

```

```{r}
m1 <- lmer(GPT ~ position + frequency + length + (frequency + length | WorkerId + element) + (0 + position + frequency + length || lemma),
  data=na.omit(data),
  REML=FALSE)

m1
```

```{r}
anova(m0, m1)
```

Based on this result, we do not include position.

#### Second check of assumptions

##### Linearity of predictors

We perform a quick visual inspection:

```{r}
plot(fitted(m), resid(m),
     xlab = "Fitted values", ylab = "Residuals")
abline(h = 0, lty = 2)
```

The cloud seems random with the exception of the lower left where we have a hard cut-off caused by the data removal that comes with Provo (\>80 ms).

Let's investigate this further:

```{r}
plot(data$length, resid(m0_log), xlab="length", ylab="Residuals"); abline(h=0,lty=2)
plot(data$frequency, resid(m0_log), xlab="frequency", ylab="Residuals"); abline(h=0,lty=2)
```

We can mitigate this problem by log-transforming the dependent variable. However, this would contradict the supposed linear effect of surprisal.

log(RT) \~ b0 + b1\*frequency + b2\*length + b3\*log(p) \<=\> RT \~ exp(b0 + b1\*frequency + b2\*length + b3\*log(p)) \<=\> exp(b0 + b1\*frequency + b2\*length)\*exp(b3\*log(p)) \<=\> b2\*length + b3\*log(p)) \<=\> exp(b0 + b1\*frequency + b2\*length)\*p\^b3

Let's try fitting log RTs.

```{r}
# Subtract by the cut-off point
data$logGPT <- log(data$GPT-80)

m0_log <- lmer(logGPT ~ frequency + length + (frequency + length | WorkerId + element) + (frequency + length || lemma),
  data=na.omit(data),
  REML=FALSE,
  control = lmerControl(calc.derivs = FALSE))

m0_log
```

```{r}
plot(fitted(m0_log), resid(m0_log),
     xlab = "Fitted values", ylab = "Residuals")
abline(h = 0, lty = 2)
```

This looks a bit better but it introduced a long tail and some artifacts.

```{r}
plot(data$length, resid(m0_log), xlab="length", ylab="Residuals"); abline(h=0,lty=2)
plot(data$frequency, resid(m0_log), xlab="frequency", ylab="Residuals"); abline(h=0,lty=2)
```

We see artifacts that are caused by frequency, probably by some very infrequent words where the wordfreq library couldn't generate a reliable measure. Therefore, we remove values smaller than 2 (TODO: zipf scale; check if this is even the proper way to generate word frequencies).

```{r}
data <- read.csv(data_dir)

# Get names of numeric columns
numeric_cols <- names(data)[sapply(data, is.numeric)]
# Subset to numeric columns you want to scale
excluded_vars <- c(goal, "WorkerId", "item", "element", "zone")
cols_to_scale <- setdiff(numeric_cols, excluded_vars)

# Apply cut-off
# Provo already comes with a minimal value of 81 for GPT
data <- apply_cutoff(data, goal)
data <- apply_cutoff(data, "frequency", lowerOther=2)

# Remove outliers
data <- remove_outliers(data, c(goal), id_col="WorkerId")

# Apply scaling
data <- data %>%
  mutate(across(all_of(cols_to_scale), scaling_var))
```

```{r}
# Subtract by the cut-off point
data$logGPT <- log(data$GPT-80)

m0_log <- lmer(logGPT ~ frequency + length + (frequency + length | WorkerId),
  data=na.omit(data),
  REML=FALSE,
  control = lmerControl(calc.derivs = FALSE))

m0_log
```

```{r}
plot(fitted(m0_log), resid(m0_log),
     xlab = "Fitted values", ylab = "Residuals")
abline(h = 0, lty = 2)
```

```{r}
plot(data$length, resid(m0_log), xlab="length", ylab="Residuals"); abline(h=0,lty=2)
plot(data$frequency, resid(m0_log), xlab="frequency", ylab="Residuals"); abline(h=0,lty=2)
```

#### Inclusion of spillover

Now, we want to determine the correct amount of spillover. We check this via a likelihood ratio test about the inclusion of spillover covariates:

```{r}
data_spill1 <- add_lags_scaled(
  lag_cols = c(frequency, length, candidates),
  group_cols = c(WorkerId, item),
  n_lags = 1
)

m0_spill1 <- lmer(GPT ~ frequency + frequency + length + position + (position + frequency + length | WorkerId+ element) + (position + frequency + length || lemma),
  data=na.omit(data_spill1),
  REML=FALSE)

m1_spill1 <- lmer(GPT ~ frequency + frequency1 + length + length1 + position + (position + frequency + frequency1 + length + length1 | WorkerId+ element) + (position + frequency + frequency1 + length + length1 || lemma),
  data=na.omit(data_spill1),
  REML=FALSE)

anova(m0, m1)
```

A final test of assumptions:
